How is experience transformed into memory?

### 2018-09-03 paper/main.tex
backing up work for the night (methods, WIP)
updated schematic figure with new version from andy
updated figs, still working on methods

\begin{figure}[tp]
\centering
\includegraphics[width=1\textwidth]{figs/analysis_schematic_bw}
\caption{\small \textbf{Methods overview.} We used hand-annotated descriptions of each moment of video to fit a topic model.  Three example video frames, and their associated descriptions are displayed (top two rows).  Participants later recalled the video (in the third row, we show example recalls of the same three scenes from one participant).  We used the topic model (fit to the annotations) to estimate topic vectors for each moment of video and each sentence the participants recalled.  Example topic vectors are displayed in the bottom row (green: video annotations; blue: example participant's recalls).  Three topic dimensions are shown (the highest-weighted topics for each of the three example scenes, respectively).  We also show the 5 highest-weighted words for each topic.  Figure~\topics~provides a full list of the top 10 words from each of the discovered topics.}
\label{fig:schematic}
\end{figure}

The topics we found were heavily character-focused (e.g., the top-weighted word in each topic was nearly always a character) and could be roughly divided into themes that were primarily Sherlock-focused; primarily John-focused (John is Sherlock's close confidant and assistant); or that involved Sherlock and John interacting (Fig.~\topics).  Several of the topics were highly similar, which we hypothesized might allow us to distinguish between subtle narrative differences (if the distinctions between those overlapping topics were meaningful; also see Fig.~\featureimportance).  The topic vectors for each timepoint were \textit{sparse}, in that only a small number (usually one or two) topics tended to be ``active'' in any given timepoint (Fig.~\ref{fig:model}A).  Further, the dynamics of the topic activations appeared to exhibit \textit{persistance} (i.e., given that a topic was active in one timepoint, it was likely to be active in the following timepoint) along with \textit{occasional rapid changes} (i.e., occasionally topics would appear to spring into or out of existence).  These two properties of the topic dynamics may be seen in the block diagonal structure of the timepoint-by-timepoint correlation matrix (Fig.~\ref{fig:model}B).  Following \cite{BaldEtal17}, we used a Hidden Markov Model (HMM) to identify the \textit{event boundaries} where the topic activations changed rapidly (i.e., at the boundaries of the blocks in the correlation matrix; event boundaries identified by the HMM are outlined in yellow).  Part of our model fitting procedure required selecting an appropriate number of ``events'' to segment the timeseries into.  We used an optimization procedure to identify the number of events that maximized within-event stability while also minimizing across-event correlations (see \textit{Methods} for additional details).  To create a stable ``summary'' of the video, we computed the average topic vector within each event (Fig.~\ref{fig:model}C).

@@

\textbf{JRM STOPPED HERE...MISSING INFO}
% don't need background or "logic"
% what was the actual optimization metric used?  e.g. what was the penalty parameter?  we should write out the optimization as an "argmax" equation...but need info from ACH about the penalty term

>>>>

\begin{figure}[tp]
\centering
\includegraphics[width=1\textwidth]{figs/schematic}
\caption{\small \textbf{Methods overview.} We used hand-annotated descriptions of each moment of video to fit a topic model.  Three example video frames, and their associated descriptions are displayed (top two rows).  Participants later recalled the video (in the third row, we show example recalls of the same three scenes from participant 13).  We used the topic model (fit to the annotations) to estimate topic vectors for each moment of video and each sentence the participants recalled.  Example topic vectors are displayed in the bottom row (green: video annotations; blue: example participant's recalls).  Three topic dimensions are shown (the highest-weighted topics for each of the three example scenes, respectively).  We also show the ten highest-weighted words for each topic.  Figure~\topics~provides a full list of the top 10 words from each of the discovered topics.}
\label{fig:schematic}
\end{figure}

The topics we found were heavily character-focused (e.g., the top-weighted word in each topic was nearly always a character) and could be roughly divided into themes that were primarily Sherlock Holmes-focused (Sherlock is the titular character); primarily John Watson-focused (John is Sherlock's close confidant and assistant); or that involved Sherlock and John interacting (Fig.~\topics).  Several of the topics were highly similar, which we hypothesized might allow us to distinguish between subtle narrative differences (if the distinctions between those overlapping topics were meaningful; also see Fig.~\featureimportance).  The topic vectors for each timepoint were \textit{sparse}, in that only a small number (usually one or two) topics tended to be ``active'' in any given timepoint (Fig.~\ref{fig:model}A).  Further, the dynamics of the topic activations appeared to exhibit \textit{persistance} (i.e., given that a topic was active in one timepoint, it was likely to be active in the following timepoint) along with \textit{occasional rapid changes} (i.e., occasionally topics would appear to spring into or out of existence).  These two properties of the topic dynamics may be seen in the block diagonal structure of the timepoint-by-timepoint correlation matrix (Fig.~\ref{fig:model}B).  Following \cite{BaldEtal17}, we used a Hidden Markov Model (HMM) to identify the \textit{event boundaries} where the topic activations changed rapidly (i.e., at the boundaries of the blocks in the correlation matrix; event boundaries identified by the HMM are outlined in yellow).  Part of our model fitting procedure required selecting an appropriate number of ``events'' to segment the timeseries into.  We used an optimization procedure to identify the number of events that maximized within-event stability while also minimizing across-event correlations (see \textit{Methods} for additional details).  To create a stable ``summary'' of the video, we computed the average topic vector within each event (Fig.~\ref{fig:model}C).

@@

\textbf{JRM STOPPED HERE...MISSING INFO}
% don't need background or "logic"
% what was the actual optimization metric used?  e.g. what was the penalty parameter?  we should write out the optimization as an "argmax" equation...but need info from ACH about the penalty term
% from slack: "for the video model its 250 and for the recall models its 50, and atm i cant recall why we chose those particular numbers."  also "well, for both numbers its 5x the window size"
